Application-Level Regression Testing Framework using Jenkins

### 2017-04-03 manuscript/manuscript.tex
Removed SWTools section.

>>>>

\section{Authenticating with One-Time Password}

Although Jenkins supplies its own authentication mechanism with its built-in user and password database, we feel that it is inadequate for securing our instance. 
The default Jenkins authentication setup is also unfortunate, in which it allows anyone to self-register creating their own username and password \footnote{This is perhaps another artifact of Jenkins setup intended to intranet environment.} 
We wanted instead to use our One-Time Password (OTP) infrastructure with RSA SecurID (FIXME: Add references https://www.rsa.com/en-us/products/rsa-securid-suite, https://en.wikipedia.org/wiki/RSA_SecurID) token for authentication. 
In this section we describe how we accomplished that.

Our use of Apache HTTP Server as front-end allow us to use ''Basic Authentication`` (FIXME: Add Reference). Via \texttt{mod_authnz_external} module, one can use any external mechanism or program to authenticate. 
One example of an authenticator is the ''pwauth`` authentication program. 
It is a simple program that returns a status code given a login (username) and password.

Combined with the Pluggable Authentication Module (PAM) --- a Unix authentication framework ---, we use ''pwauth`` to authenticate against our RSA SecurID OTP infrastructure. 
This is set up in the file \texttt{/etc/pam.d/pwauth}:
\begin{lstlisting}
#%PAM-1.0
auth	   required	/lib64/security/pam_securid.so
account    include      password-auth
\end{lstlisting}

Jenkins can use the user information given by Apache HTTP server if one selects ''HTTP Header by reverse proxy`` for its security realm. 
This means that all authentication is handled by Apache. 
Authenticating directly to \texttt{pwauth} against RSA SecurID OTP however presents an issue. 
It is often the case that a request needs to re-authenticate. 
The web browser normally handles this seamlessly by caching the user's credentials.
However, this does not work since, by definition, OTP credentials can only be used once. 
The solution is to use a back-end authenticator with some form of session management.

To accomplish this, we wrote a small python script called ''BasicAuthOTPSession`` [FIXME: Add Reference] as the authentication mechanism, wrapping the real authenticator (i.e. \texttt{pwauth} with PAM for RSA SecurID in our case). 
For the first time, it calls the real authenticator. 
Once an authentication succeed, a session is created and the next request with the same credentials from the same IP address are deemed successful without going through the real authenticator. 
The session expires in a predefined amount of time. 
A new request within that time renew the session. 
If there is no more request within that time, the session expires.
When this happens, one has to authenticate again with the real authenticator.

Figure {FIXME: CREATE FIGURE) illustrates the authentication mechanism we describe. 
Most of the configuration is defined in the file \texttt{/etc/httpd/conf.d/ssl.conf}, immediately following listing [FIXME: CITE LISTING] inside the same \texttt{<VirtualHost>} directive:

\begin{lstlisting}
#-- OTP for Jenkins SSL connection
DefineExternalAuth pwauth+session pipe /usr/local/bin/BasicAuthOTPSession.py

<LocationMatch / > 
  AuthType Basic
  AuthBasicProvider external
  AuthName "NCSA RSA OTP login" 
  AuthExternal pwauth+session
  require valid-user  
  RequestHeader unset "X-Forwarded-User"
  RequestHeader set "X-Forwarded-User" (REMOTE_USER)
</LocationMatch>

\end{lstlisting}
The \texttt{<LocationMatch / >} directive ensures that every request to the secure HTTP site is authenticated.
